Analyzing Coopetition Strategies of Services within Communities

### 2012-11-25 papers/coopv2/ICSOC Submission/ICSOC 2012.tex
Changes

@@

\begin{figure}%[h]
\centering
\includegraphics[scale=0.31]{Graph2.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}
average of web services that can get a task when the coopetitive
strategy is followed. We observe that in different runs, this
percentage is generally increasing. This shows that over runs the
web services get to learn the threshold $\tau_w^t$ that allows
them to select the good strategy. We should notice that in
different runs different initial values of the threshold are used
ranging from $0.3$ for run 1 to $0.6$ for run 4.

@@

>>>>

\begin{figure}%[h]
\centering
\includegraphics[scale=0.31]{Graph2.eps}
\caption{Competitive and cooperative probabilities regarding four
different web services.} \label{Graph2}
\end{figure}

@@

@@

We conclude out analysis by discussing how well our cooperative decision making process is by comparing the final utility of our agents here the end budget our webservices have while deviating from our strategy adopted by an agent which can be either compete or cooperate to the other one. In \ref{graph_dev} part (a) we randomly made the web services deviate from the calculated strategy. As the results depict, the more web services deviate from cooperative strategy the more they less budget they gain. Figure \ref{graph_dev} part (b) we pick one random webservice and once simulate the scenario with its default cooperative strategy and then we redo the simulation with exact same enviroment parameters while adapting the other strategy which is to compete if our cooperative strategy suggested to cooperate or vise versa. We run this 50 times and at the end we check their budget and see if they gain more by deviating or not. We did this for one single deviation to ten different deviations in lifetime of a web service in community. As results indicate with high probability our cooperative strategy yields higher budgets at the end for web services.
